---
title: "My coding in Data Analytics"
date: '2021-10-20'
description: Coding in R
draft: no
image: ''
keywords: ''
slug: coding
categories:
- ''
- ''
---

```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, echo=FALSE, warning=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(GGally)
library(readxl)
library(here)
library(skimr)
library(janitor)
library(broom)
library(tidyquant)
library(infer)
library(openintro)
library(kableExtra)
```

These are a few graphs I worked on as part of a homework for the Data Analytics in Finance course:

***
First, we will load the yield curve data file that contains data on the yield curve since 1960-01-01

```{r download_historical_yield_curve, warning=FALSE}

yield_curve <- read_csv(here::here("data", "yield_curve.csv"))

glimpse(yield_curve)
```

Our dataframe `yield_curve` has five columns (variables):

- `date`: already a date object
- `series_id`: the FRED database ticker symbol
- `value`: the actual yield on that date
- `maturity`: a short hand for the maturity of the bond
- `duration`: the duration, written out in all its glory!


## Plotting the yield curve

### Yields on US rates by duration since 1960

```{r}
yield_curve  %>% 
  mutate(duration=factor(duration, levels=c("3-Month Treasury Bill", "6-Month Treasury Bill","1-Year Treasury Rate","2-Year Treasury Rate","3-Year Treasury Rate","5-Year Treasury Rate","7-Year Treasury Rate","10-Year Treasury Rate","20-Year Treasury Rate","30-Year Treasury Rate"))) %>% 
  
  ggplot(aes(x=date, y=value, color=duration)) +
  geom_line()+
  facet_wrap(~ duration, ncol=2)+
  labs(title="Yields on U.S. Treasury rates since 1960",
       y="Yield(%)",
       x="Date",
       caption="Source: St. Louis Federal Reserve Economic Database (FRED)")+
  theme_bw()+
  theme(legend.position="none")

```


### Monthly yields on US rates by duration since 1999 on a year-by-year basis

```{r}
yield_curve_2 <- yield_curve  %>%
  mutate(year=factor(year(date)), 
         maturity=factor(maturity, levels=c("3m", "6m","1y","2y","3y","5y","7y","10y","20y","30y")))

yield_curve_2 %>%
  filter(date>="1999-01-01") %>% 
  ggplot(aes(x=maturity, y=value, group=date, color=year)) +
  geom_line()+
  facet_wrap(~ year, ncol=4)+
  labs(title="U.S. yield curve",
       y="Yield(%)",
       x="Maturity",
       caption="Source: St. Louis Federal Reserve Economic Database (FRED)")+
  theme_bw()+
  theme(legend.position="none")

```


### 3-month and 10-year yields since 1999

```{r treasury_rates}

yield_curve_3 <- yield_curve %>% 
  filter(date>="1999-01-01", maturity =="3m" | maturity =="10y") %>%
  ggplot(aes(x=date, y=value, color=duration, group=maturity))+
  geom_line()+
  theme_bw()+
  theme(legend.title=element_blank())+
  labs(title="Yields on 3-Month and 10-Year U.S. Treasury Rates since 1999",
       y="Yield(%)",
       x="Date",
       caption="Source: St. Louis Federal Reserve Economic Database (FRED)")
yield_curve_3
```

